A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population

### 2017-07-16 referee_response.txt

General comments:

We thank the referee for a thorough review and suggestions for improvement.

@@

Responses start with ">>>"

==================
Responses to the editors
==================

@@

Please also use the full references for the items noted under the \software command, e.g.

emcee (Foreman-Mackey et al. 2013)

>>> Done. Thanks for the reminder.

>>> We left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".

============
Responses to the referee
============

Referee Report
Reviewer's Comments:
This paper presents a multi-year observing campaign with the VLA telescope to study the repeating pulses from FRB 121102. Many VLA observations were also simultaneous with observations at radio telescopes observing at other frequencies. In some cases pulses detected at the VLA were not detected at higher or lower frequencies and in one case a pulse was detected with both the VLA and the Arecibo Observatory and this information as well as the pulse spectra from the VLA can be used to constrain the emission properties of this source as well as a burst rate. This work is very interesting, and well-presented, and crucial for our understanding of FRB 121102 in specific, but also the possible properties of fast radio bursts in general.

@@

I think this work is worthy of publication in the journal with moderate revision of the manuscript. Some moderate revision of the text is needed (see below) as well as some structural and conceptual changes. I have included my comments on the manuscript below with general large comments (1, 2, 3..) on the paper at the beginning, and major (A, B, C,...) and minor (i, ii, iii,...) comments per section.

General comments on the manuscript:

1. Throughout the text it is mentioned that this is the first simultaneous detection of an FRB pulse at multiple observatories, but I don't believe this is correct. The observations detailed in Marcote et al. 2017 include VLBI observations of individual pulses from FRB 121102 detected at different observatories. In that sense, this paper does not present the first simultaneous detection. Perhaps the authors mean first simultaneous detection at multiple radio frequencies, but if this is the case this statement should be revised throughout the manuscript.

>>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September. The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first. I would prefer to keep the current wording.

@@

Equation 1: A is typically used for a unitless amplitude, but in this case is given in units of flux density. If this value is indeed meant to be the flux density of the pulse then $S$ should be used as the symbol for flux density instead of A.

>>> Done.

A. Paragraph beginning "The parameters for the best model ... " : Your fits to the pulse spectra seem to indicate that all but two of the VLA burst detections are well-modeled by a Gaussian envelope completely contained within the 3 GHz band. How likely is this? It seems to be implying that 3 GHz was the perfect frequency at which to center your observations. While this seems fortunate it doesn't make immediate physical sense to me. I might have expected some uniformly broadband pulses, some with an envelope within your observing band, and some with an envelope that extends beyond the observing band, but you find that most are described by an entirely in-band envelope. Is this physical or could this be an artefact of the model fits you have applied to the data? If you believe that this is indeed an intrinsic effect I would like to see more discussion of the physical mechanism behind the very fortunate 3 GHz observing window.

>>> My interpretation is that this is a detection bias and has no physical meaning. If the bursts have a peak in their spectrum, then it is easiest to detect bursts with a peak inside the observing band. Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance. 
>>> I'm not sure how to discuss this in the text, but I'd welcome suggestions.

@@

i. For clarity, please label the rates at different observing frequencies in the text as $R_{3 GHZ}$ etc.

ii. Equation 3: Similar to Equation 1, A is given in units of flux density and should therefore be represented by the symbol $S$.

iii. dN/d logE : Elsewhere in the text this is written as dN/dE. Please be consistent in notation.

>>> Done. On the last point, the distinction between dN/d logE and dN/dE was deliberate, but we tried to avoid confusing readers. The issue is that we modeled the distribution in log space, but these kinds of results are typically discussed in linear space. Since the analysis is publicly available (Jupyter notebooks on github), I wanted to maintain some reference to the details of the analysis in the text. I can't do that without redoing the analysis approach entirely, as shown in the notebook.

@@

ii. "At the typical Parkes ... at $z \approx 1$" : Please clarify this statement. Do you mean that a Parkes survey could detect the brightest pulse from FRB 121102? The brightest X pulses? The discovery pulse (I think this one was too weak for Parkes)? The "average" pulse?

>>> Reworded. The largest burst energy detected by the VLA was 10^40, which is detectable by the typical Parkes survey at z=1.

iii. "understated by a factor of a few by ignoring bursts that fall outside the observing band" : The data presented in this paper are the best currently available to actually constrain this factor. Would it be possible to provide an estimate of this factor using the detections/non-detections from these observations?

>>> I do not believe that these data can address this question. We have identified a quasi-broadband structure for burst spectra and have shown that detection of a burst at one frequency does not predict the detection of that same burst at another frequency. As we discuss, an implication of this is that the burst rate cannot be defined from any single observing band.
>>> We are working on a comprehensive analysis of the Arecibo data (at 1.4 GHz) during this observing period. The joint consideration of the VLA and AO burst rates, along with their time and luminosity distributions, will be required to estimate this "true" burst rate.

@@

iv. "$5 \times 10^2$ and $5 \times 10^3$ times" : Is this range of repetition times sufficient for the repeater? In the observations from just the past 1 year this FRB has emitted O[100] pulses, I believe, and was active at least back to 2012, possibly much longer. Have you or others in the FRB 121102 team attempted to estimate the total number of pulses this FRB may have given off assuming this activity? In doing this does this particular source still fall in the range you've given here? If so, it is worth mentioning where you believe FRB 121102 falls in this range.

>>> Good point. We've split the last paragraph in two and added some discussion on this point.

### 2017-07-16 repeater-vladata.tex
working through stickier poitns

We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. The flux density of the Arecibo burst detected on MJD 57648 is an order of magnitude less than that seen by the VLA. At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously. This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz. This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S, 2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.

@@

Despite its many assumptions, this volumetric birth rate is more appropriate for comparison to rates used for other classes of transient. The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}. Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively. This assumes isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg. \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$. This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.

@@

The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined. That fact, combined with a rich data set of many bursts, allows us to apply this source to more general questions about the FRB population.

>>>>

We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. The flux density of the Arecibo burst detected on MJD 57648 is an order of magnitude less than that seen by the VLA. At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously. This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz. This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S, 2016arXiv160308880S} with a wider bandwidth and extends the existence of this phenomenon to 3~GHz.

@@

Despite its many assumptions, this volumetric birth rate is more appropriate for comparison to rates used for other classes of transient. The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}. Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times. This is consistent with a related rate comparison presented in \citet{2017arXiv170400022N}. Here, we have assumed isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg.

\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$. This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate. Under that model, \frb\ could emit bursts for roughly 400 days at the peak burst rate measured by the VLA. Continued monitoring of \frb\ bursts will continue to be useful in testing models for FRB origin.

@@

The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical sources. With its cosmological distance firmly established and a rich data set of many bursts, \frb\ serves as a prototype that can be used to infer properties of the larger FRB population.
